\documentclass[]{cv}

\begin{document}

%\namesection{Rasmus}{Wejlgaard}{\urlstyle{same}\url{https://pez.sh} \\
%\href{mailto:pez@pez.sh}{pez@pez.sh} \\ 
%+447570186729
%}

\begin{minipage}[t]{0.33\textwidth} 

\section{Education} 

\subsection{TEC}
\descript{Bachelor in Computer Science}
\location{2013 - 2018}
\location{Copenhagen, DK}
\sectionsep

\subsection{Public School}
\location{2003 - 2013}
\location{V\ae rl\o se, DK}
\sectionsep

\section{Links} 
Github: \href{https://github.com/rwejlgaard}{\custombold{rwejlgaard}} \\
% WhatsApp:// \custombold{+447570186729} 
Personal Webiste: \href{https://pez.sh}{\custombold{https://pez.sh}} \\
Side-project Website:  \href{https://pez.solutions}{\custombold{https://pez.solutions}} \\
\sectionsep

\section{Skills}
\subsection{Personal}

\location{Working:}
\vspace{\topsep}
\begin{tightemize}
	\item I'm hard working,\\ as long as there's work I'm happy
	\item I strive for perfection in my work
	\item I enjoy helping my colleagues
\end{tightemize}
\location{Non-Working:}
\begin{tightemize}
	\item Great at dad jokes
	\item I once killed a fly with a rubber band
\end{tightemize}
\sectionsep

\subsection{Technologies}

\location{Stack:}
\begin{tightemize}
	\item Linux
	\item Docker
	\item CI/CD
	\item Jenkins
	\item Istio
	\item Google Cloud
	\item AWS
	\item Saltstack
	\item Ansible
	\item Splunk
	\item Terraform
	\item Kubernetes
	\item Cloudflare
\end{tightemize}
\sectionsep

\section{Programming}
\location{Excellent:}
Python \textbullet GO
\sectionsep	

\location{Really Good:}
C\# \textbullet C++ \textbullet Java
\sectionsep

\location{Pretty Good:}
C \textbullet Rust \textbullet Swift \textbullet Obj. C \textbullet JavaScript
\sectionsep

\location{Played around with:}
TypeScript \textbullet Android

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

\section{Experience}

\runsubsection{Expedia Group}
\descript{| Senior Platform Engineer | Contract}
\location{October 2022 - Present | London, UK}

\location{Description:}
My first contract role, I help manage Expedias massive cloud infrastructure footprint. \\
With a 3 digit number of Kubernetes clusters. It's no easy task to maintain operation and maintainability. \\
I'm part of the team that is responsible for the operation of the clusters. A team comprised of 3 locations across the world.
\sectionsep

\runsubsection{GoHenry}
\descript{| Senior Platform Engineer}
\location{March 2021 - October 2022 | London, UK}

\location{Description:}
I joined GoHenry to continue my career in fintech. 
Now as a senior engineer I had taken on more responsibility. 
I shared complete responsibility of the cloud infrastructure with the lead engineer in the
platform team. 
My main responsibility was around Kubernetes, where I ensured the most reliable operation for
hosting 800 microservices across 4 clusters. 
In my time there I had been in the lead of migrating onto the Istio serivcemesh from
NGINX-ingress with zero downtime during the entire migration. 
We originally had 8 clusters, 2 for each project with a cluster in the US and a cluster in the
UK. Which was merged together during the migration to Istio with zero downtime as well.
\sectionsep

\runsubsection{10x}
\descript{| Site Reliability Engineer}
\location{September 2019 - March 2021 | London, UK}

\location{Description:}
After moving to the UK in August 2019, I joined 10x. \\
10x is a Bank-as-a-Service company, 10x has numerous tier 1 banks as clients. \\
As an SRE, I worked on maintaining operational excellence for our clients. \\
This was done utilizing the latest technologies in Kubernetes and cloud native architecture. \\
A few key technologies we used were the likes of Prometheus/Grafana, Splunk, Helm, Terraform, and Concourse CI. \\
The job required a flexible mind and I often jumped back and forth between "Proactive" and "Reactive" workloads. \\
The Reactive side involved fixing various issues such as severity 1/2 incidents, with a focus on efficiency and speed. \\
The job also required on-call shifts which we used alertmanager and PagerDuty for.
\sectionsep

\runsubsection{Widex}
\descript{| Software Delivery Engineer}
\location{Oct 2018 - April 2019 | Lynge, Denmark}

\location{Description:}
After finishing my education I was approached by a recruiter from Widex. \\
I was hired in October of 2018, into the SWISS team - which is short for Software \& Infrastructure Services. \\
The teams objective was to make the developers jobs as smooth as possible. \\
This meant maintaining the 3 major build pipelines for iOS, Android and Windows-Desktop. \\
Automate lesser tasks such as miscellaneous tasks for git or Jira. \\
After about 4 months of working at Widex, I was given the responsibility to automate the provisioning of our build server farm. \\
My last two months at Widex I worked on automating deployments of new build machines \\
Used Golang for creating an exporter of Jenkins data into Prometheus
\sectionsep

\runsubsection{KMD}
\descript{| Cloud Platform Engineer }
\location{Dec 2015 - Sep 2018 | Ballerup, Denmark}

\location{Description:}
This was my first job, I was originally hired as a trainee Java developer but I ended up moving
to the platform team after a year. \\
In the platform team I was one of two engineers maintaining the ”PaaS Engine” which
purpose was to work like an internal cloud provider, providing EC2/Compute instances to
internal projects. The project used Python and Saltstack very heavily to automate and
provision servers from our bare-metal datacenter. \\
I learned most of what I know from this project and I taken off the project when the project
was bought by IBM Cloud.
\sectionsep

\end{minipage} 
\end{document}
